Missing The Point

### 2020-09-18 Manuscript.Rmd
Include data generation in each simulation rep, to suit the regular CI computation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results.Rdata")

@@

```{r echo=FALSE}
results %>%
  ggplot() +
  geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  geom_hline(yintercept = 0.95) +
  geom_point(aes(x=it, y=cov, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=cov, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  geom_hline(yintercept = 0.2090) +
  geom_point(aes(x=it, y=rsq, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=rsq, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```
```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.sigma.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.sigma.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
load("~/MissingThePoint/Data/results_standard_ci.Rdata")

@@

```{r echo=FALSE}
results %>%
  ggplot() +
  #geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  #geom_hline(yintercept = 0.95) +
  geom_point(aes(x=it, y=cov, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=cov, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  #geom_hline(yintercept = 0.2090) +
  geom_point(aes(x=it, y=rsq, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=rsq, color = mech, linetype = as.factor(p))) +
  theme_classic()

@@

```{r}
results %>%
  ggplot() +
  geom_point(aes(x=it, y=ac.max.sigma.Y, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=ac.max.sigma.Y, color = mech, linetype = as.factor(p))) +
  theme_classic()
```
